Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-08 paper/paper.tex
Typo, missing figure, config
Add some descriptive stats

We recruited 41 participants from Amazon Mechanical Turk (AMT), a common tool to run perception studies for visualizations~\cite{heer2010crowdsourcing}.
Similar to other studies of human perception of visualizations, we restricted participation to people on AMT with at least 1,000 tasks completed and an approval rate above 95\%.
Participation was restricted to the United States to ensure familiarity with the airlines and states in the dataset.
Participants were compensated \$2.00 for completing the study.

@@

We refer to this value as the \textbf{expected bias}.
We treat the expected bias as an independent variable in our analysis.
We hypothesized that the greater the expected bias, thr greater the measured bias would be.
Meaning, if an approximate visualization differed substantially from the precise visualization, we expected participant's answers to be close to correct (e.g., a measured bias of near 0), but skew in the direction of the approximate visualization.
We anticipated that the measured bias would be less than the expected bias, as participants had seen the updated, correct visualization.

@@

\todo{Summary demographics about our participants, who we dropped, etc.}

>>>>

We recruited 34 participants from Amazon Mechanical Turk (AMT), a common tool to run perception studies for visualizations~\cite{heer2010crowdsourcing}.
Similar to other studies of human perception of visualizations, we restricted participation to people on AMT with at least 1,000 tasks completed and an approval rate above 95\%.
Participation was restricted to the United States to ensure familiarity with the airlines and states in the dataset.
Participants were compensated \$2.00 for completing the study.

@@

We refer to this value as the \textbf{expected bias}.
We treat the expected bias as an independent variable in our analysis.
We hypothesized that the greater the expected bias, the greater the measured bias would be.
Meaning, if an approximate visualization differed substantially from the precise visualization, we expected participant's answers to be close to correct (e.g., a measured bias of near 0), but skew in the direction of the approximate visualization.
We anticipated that the measured bias would be less than the expected bias, as participants had seen the updated, correct visualization.

@@

We recruited 40 participants for the study.
One did not complete the study and 5 participants had to be removed because they said they cheated during the study.
We used the data from the remaining 34 participants for our analysis.

The average participant was 33.7 years old.
26 participants self-identified as male and 8 as female.
All participants reported that they had no technical problems with the study procedures.
Only 11\% of our participants said they are not with all of these visualization types: barcharts, scatterplots, and heatmaps.
On average participants spent 8 minutes on the study with 3:20 minutes standard deviation.
As expected, most participants spent more time on the questions than the visualizations and overall the most time on the questions about the precise data.
